Connecting scene direction to year and writer

### 2017-06-18 connect_year_writer.Rmd
Modeling change by year

```{r, dependson="pronoun_imdb"}
pronoun_imdb %>%
    inner_join(metadata, by = "imdb") ## to get year

@@

>>>>

```{r, dependson="pronoun_imdb"}

@@

## Change by year

```{r words_by_year, dependson="pronoun_imdb"}
words_by_year <- pronoun_imdb %>%
    inner_join(metadata, by = "imdb") %>% ## to get year
    filter(word1 == "she",
           str_detect(word2, "[a-z]+"),
           nchar(word2) > 2,
           !is.na(year),
           year > 1980) %>%
    mutate(year = 5 * year %/% 5) %>%
    add_count(year) %>%
    rename(year_total = n) %>%
    add_count(word2) %>%
    rename(word_total = n) %>%
    filter(word_total > 50) %>%
    count(word2, year, year_total)

slopes <- words_by_year %>%
    nest(-word2) %>%
    mutate(models = map(data, ~ glm(cbind(n, year_total) ~ year, ., 
                                    family = "binomial"))) %>%
    unnest(map(models, tidy)) %>%
    filter(term == "year") %>%
    arrange(estimate)
```

```{r contractions, dependson="words_by_year", fig.width=7, fig.height=5}
words_by_year %>%
    inner_join(slopes %>%
                   top_n(10, estimate), 
               by = "word2") %>%
    ggplot(aes(year, n / year_total, color = word2)) +
    geom_line(alpha = 0.8, size = 1.3) +
    labs(x = NULL, y = "Word frequency",
         title = "Words paired with 'she' in script set directions",
         subtitle = "Many of the words increasing in frequency with time are negative contractions")
```

```{r increasing, dependson="words_by_year", fig.width=7, fig.height=5}
words_by_year %>%
    inner_join(slopes %>%
                   filter(str_detect(word2, "^[^’]*$")) %>%
                   top_n(10, estimate), 
               by = "word2") %>%
    ggplot(aes(year, n / year_total, color = word2)) +
    geom_line(alpha = 0.8, size = 1.3) +
    labs(x = NULL, y = "Word frequency",
         title = "Words paired with 'she' in script set directions",
         subtitle = "More recently, women are more likely to inspect, drift, steal, exhale,  breathe")
```

```{r decreasing, dependson="words_by_year", fig.width=7, fig.height=5}
words_by_year %>%
    inner_join(slopes %>%
                   top_n(-10, estimate), 
               by = "word2") %>%
    ggplot(aes(year, n / year_total, color = word2)) +
    geom_line(alpha = 0.8, size = 1.3) +
    labs(x = NULL, y = "Word frequency",
         title = "Words paired with 'she' in script set directions",
         subtitle = "In the past, women were more likely to jab, snuggle, fling, whirl, shriek")
```
